Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-05 WSSSPE3/report/WSSSPE3_review.tex
add Birgit's talk summary

\begin{enumerate}
\item \textbf{Benjamin Tovar and Douglas Thain: \textit{Freedom vs. Stability:
Facilitating Research Training While Supporting Scientific Research}}

@@

\item \textbf{Jeffrey Carver: \textit{On the Need for Software Engineering Support for
Sustainable Scientic Software}}

I argue that for scientific software to be truly sustainable, there is a need
for developers to use appropriate software engineering practices. My experience
interacting with scientific teams indicates that choosing and tailoring these
practices is not a trivial exercise. There is a general culture clash between
software engineering and science that hinders our ability to communicate and
choose appropriate methods. In addition, many experience scientific software
developers appear to be unaware of software engineering practices that may be
beneficial to them. The most appropriate software engineering practices are
those that are lightweight, properly tailored, and focus on the key software
development problems faced by scientists. In order to increase the use of
software engineering in science, we need more documented success stories. These
successes need to be socialized within the scientific community through
workshops like the Software Engineering for Science workshop
series~\footnote{\href{http://www.SE4Science.org/workshops}{http://www.SE4Science.org/workshops}}
and the new Software Engineering track in
Computing in Science and Engineering magazine.

>>>>

\begin{enumerate}
\item \textbf{Benjamin Tovar and Douglas Thain: \textit{Freedom vs. Stability:
Facilitating Research Training While Supporting Scientific Research}}
A case study: ``The Cooperative Computing Lab'' at the University of Notre Dame
is a small group of individuals with the main tasks of collaborating with
people that have large-scale computing problems, operating various parallel
computer systems, conducting computer science research, and developing open
source software. One of the main challenges they face is finding the balance
between flexibility/training and stability/quality. Their current solution for
ensuring the latter was to add a software engineer (the presenter) to the
existing team of faculty and students, who now also serves as ``spring''
between flexibility and stability.

@@

\item \textbf{Jeffrey Carver: \textit{On the Need for Software Engineering Support for
Sustainable Scientic Software}}
I argue that for scientific software to be truly sustainable, there is a need
for developers to use appropriate software engineering practices. My experience
interacting with scientific teams indicates that choosing and tailoring these
practices is not a trivial exercise. There is a general culture clash between
software engineering and science that hinders our ability to communicate and
choose appropriate methods. In addition, many experience scientific software
developers appear to be unaware of software engineering practices that may be
beneficial to them. The most appropriate software engineering practices are
those that are lightweight, properly tailored, and focus on the key software
development problems faced by scientists. In order to increase the use of
software engineering in science, we need more documented success stories. These
successes need to be socialized within the scientific community through
workshops like the Software Engineering for Science workshop
series~\footnote{\href{http://www.SE4Science.org/workshops}{http://www.SE4Science.org/workshops}}
and the new Software Engineering track in Computing in Science and Engineering
magazine.
